---
title: "R101 Exercises"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1.

Open [RStudio IDE](https://www.rstudio.com/products/rstudio/) on your desktop or alternatively use [RStudio Cloud](https://www.rstudio.com/products/rstudio/)

- Create a new R Script from the menu bar: 'File > New File > R Script'.

- Save the new R Script file to a new directory location. Example file path: R Workshops/R101/Exercises/Exercise_1.R
    

- Using the editor window, enter the following command to assign a value to the variable <i>'x'</i>. Note the use of the assignment symbol <i><-</i>.

```{r eval=TRUE }
   x <- 24
```

- Type <i>'x'</i> at the command prompt in the console window and hit return 'key' to print the output.

```{r comment='#'}
   x 
```


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
